The benefits of an extended feature space in a machine learning bot for the game Schnapsen

### 2018-02-01 Text/paper.tex
Added a little bit of information to findings/rdeep

\subsection*{Against Rdeep}
The \textit{standard deviation} of the mean of the 9 tournaments for each bot against rdeep is 0.02804758.
First of all, the learning bots performed worse than rdeep. The worst performer was, surprisingly, the stock ml bot. However, the results of the bots are relatively close, except for the ml\_minimal bot.

>>>>

\subsection*{Against Rdeep}
The \textit{standard deviation} of the mean of the 9 tournaments for each bot against rdeep is 0.02804758. This number is the lowest of all the non-learning bots and is clearly confirmed by the barplot in figure 3. Rdeep won the majority of the games, which results in a low diversity of winning scores among the learning bots. The worst performer was, surprisingly, the stock ml bot. The only bot  results of the bots are relatively close, except for the ml\_minimal bot. WIP
